Growing Up With Nell: A Narrative Interface for Literacy

### 2012-04-23 paper.tex
Alternate non-quasi-quote template syntax.
This uses ${} so that it's compatible with quasi-quote in the future.
ie, eventually "${foo}" might become `${foo}`.
Formatting tweaks for final submission.
Quote keys in JSON (these are optional in JS, but mandatory in JSON).

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
%
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%\documentclass{acm_proc_article-sp}
\documentclass[preprint]{sig-alternate}
\usepackage{url}
\usepackage{ifthen}\newboolean{noauthors}\setboolean{noauthors}{true}
\hyphenation{Web-GL Java-Script Turtle-Script infra-structure}

@@

\title{Growing Up with Nell: A Narrative Interface for Literacy}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

@@

\subsection{Rule-based story modules}
\begin{figure}\small
\begin{verbatim}
{ world: { // id gives canonical URL for this module
    id: "/nell.laptop.org/chapters/alphabet-book",
    scene: "opening", // initial scene
    inherit_from: "/nell.laptop.org/core/drawing_activity",
  }, scenes: [
    { id: "opening", subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Hello! Would (o/2) like to hear a story?",
      group: "/nell.laptop.org/core/story-intro-group",
    },
    { id: "story-1",
      cond: rule`At(opening) && Event(Chat, Yes)`,
      subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Once upon a time..." },
    ...
    { id: "r-drawn",
      cond: rule`Event(Activity, DrawR)`,
      subject: "actors/princess",
      verb: "speak", object: "actors/user",
      text: "Very good, (o/3)!",
      action: js`startAnimation("r-runs")` }, ...
  ], ... }
\end{verbatim}
\caption{Excerpt of story module.  JSON syntax has been extended with
quasiquote~\cite{quasiquote}.}\label{fig:rules}
\end{figure}
To implement Nell's modular narrative interface, we use a
production rule system with programmable conflict resolution.
Figure~\ref{fig:rules} shows
an excerpt of the story module underlying the interaction described in
Section~\ref{sec:lesson}.

@@

\begin{figure}\small
\begin{verbatim}
{ aiml: {
  version: "1.0",
  categories: [
    { pattern: "GO *",
      template: "{*}" },
    { pattern: "N",
      template: "{NORTH}" },
    { pattern: "NORTH",
      template: js`FireEvent(Chat, "NORTH")` },
    { pattern: "* THE DOOR",
      template: "{*} DOOR" },
    { pattern: "* SQUEAKY DOOR",
      template: "{*} DOOR" },
    { pattern: "OPEN DOOR",
      template: js`FireEvent(Chat, "OPEN DOOR")` }
  ] } }
\end{verbatim}
\caption{An AIML fragment which recognizes the commands
  %\texttt{N},
  \texttt{North}, \texttt{Go North}, \texttt{Open the squeaky door}
  and variants.  AIML's XML syntax has been translated to JSON.
  Template contents in braces invoke the recognizer recursively
  (what AIML calls \texttt{<srai>}).
% XXX: how to handle multiple stars?  In XML, it's <star index="1">
}\label{fig:aiml}
\end{figure}

>>>>

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
%
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%\documentclass{acm_proc_article-sp}
\documentclass[preprint]{sig-alternate}
\usepackage{url}
\usepackage{ifthen}\newboolean{noauthors}\setboolean{noauthors}{false}
\hyphenation{Web-GL Java-Script Turtle-Script infra-structure}

@@

\title{Growing Up With Nell: A Narrative Interface for Literacy}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

% Copyright info
\toappear{\textit{IDC 2012}, June 12--15, 2012, Bremen, Germany.\\
Copyright 2012 ACM 978-1-4503-1007-9\ldots\$10.00.}

@@

\subsection{Rule-based story modules}
\begin{figure}\small
\begin{verbatim}
{ "world": { // id gives canonical URL for this module
    "id": "/nell.laptop.org/chapters/alphabet-book",
    "scene": "opening", // initial scene
    "inherit_from": "/nell.laptop.org/core/drawing_activity",
  }, "scenes": [
    { "id": "opening", subject: "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Hello! Would (o/2) like to hear a story?",
      "group": "/nell.laptop.org/core/story-intro-group",
    },
    { "id": "story-1",
      "cond": rule`At(opening) && Event(Chat, Yes)`,
      "subject": "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Once upon a time..." },
    ...
    { "id": "r-drawn",
      "cond": rule`Event(Activity, DrawR)`,
      "subject": "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Very good, (o/3)!",
      "action": js`startAnimation("r-runs")` }, ...
  ], ... }
\end{verbatim}
\caption{Excerpt of story module.  JSON syntax has been extended with
quasiquote~\cite{quasiquote}.}\label{fig:rules}
\end{figure}
To implement Nell's modular narrative interface, we use a
production rule system with programmable conflict resolution.
Figure~\ref{fig:rules} shows
an excerpt of the story module underlying the interaction described in
Section~\ref{sec:lesson}.

@@

\begin{figure}\small
\begin{verbatim}
{ "aiml": {
  "version": "1.0",
  "categories": [
    { "pattern": "GO *",
      "template": "{*}" },
    { "pattern": "N",
      "template": "{NORTH}" },
    { "pattern": "NORTH",
      "template": js`FireEvent(Chat, "NORTH")` },
    { "pattern": "* THE DOOR",
      "template": "{*} DOOR" },
    { "pattern": "* SQUEAKY DOOR",
      "template": "{*} DOOR" },
    { "pattern": "OPEN DOOR",
      "template": js`FireEvent(Chat, "OPEN DOOR")` }
  ] } }
\end{verbatim}
% alternate template syntax, compatible w/ quasiquote but not
% dependent on it:
% template: "${srai(star(0))}" // can be abbreviated as srai(star()) or srai()
% template: "${srai("NORTH"}}"
% template: "${FireEvent(Chat, "NORTH")}"
% template: "${srai()} DOOR" // abbreviation for srai(star(0))
\caption{An AIML fragment which recognizes the commands
  %\texttt{N},
  \texttt{North}, \texttt{Go North}, \texttt{Open the squeaky door}
  and variants.  AIML's XML syntax has been translated to JSON.
  Template contents in braces invoke the recognizer recursively
  (what AIML calls \texttt{<srai>}).
% XXX: how to handle multiple stars?  In XML, it's <star index="1">
}\label{fig:aiml}
\end{figure}
